R für die sozio-ökonomische Forschung

### 2020-12-06 title.tex

\begin{titlepage}
\BgThispage
\newgeometry{top=3.0cm,left=1cm,right=4cm}
\vspace*{2cm}
\noindent
\onehalfspacing
\textcolor{white}{\bigsf R für die \mbox{sozio\"okonomische} Forschung}
\vspace*{1.2cm}\par
Aktuelle Version: 0.7.1 (\today)\\
\vspace*{2.0cm}\par
\noindent
\begin{minipage}{0.35\linewidth}
    \begin{flushright}
        \printauthor
    \end{flushright}
\end{minipage} \hspace{15pt}
%
\begin{minipage}{0.02\linewidth}
    \rule{1pt}{175pt}
\end{minipage} \hspace{-10pt}
%
\begin{minipage}{0.6\linewidth}
\vspace{5pt}
\begin{adjustwidth}{25pt}{25pt}
\raggedright
Dieses Skript begleitet die Lehrveranstaltung `Methoden der Sozio\"okonomie` von
Prof. Jakob Kapeller und Dr. Claudius Gr\"abner im Master `Sozio\"okonomie` an der
Universit\"at Duisburg-Essen im Wintersemester 2019/20.

Feedback \"uber Moodle oder
\href{https://github.com/graebnerc/RforSocioEcon}{Github} ist
sehr willkommen.
\end{adjustwidth}

\end{minipage}

\vspace{0.25cm}
\centering
\vspace{1.25cm}
\textbf{Wintersemester 2019/2020}\\
\vfill
\includegraphics[height=2cm]{figures/ifso_logo_dt_RGB} \hspace{2cm}
\includegraphics[height=2cm]{figures/logo_ude.pdf}
\end{titlepage}

% comment
\newpage
\pagenumbering{arabic}

>>>>

%\begin{titlepage}
\BgThispage
% \newgeometry{top=3.0cm,left=1cm,right=4cm}

\definecolor{titleback}{RGB}{50,140,50}

%\begingroup
%\thispagestyle{empty}
\begin{tikzpicture}[remember picture,overlay]
\coordinate [below=10cm, right=2cm] (midpoint) at (current page.north);
\node at (current page.north west)
{\begin{tikzpicture}[remember picture,overlay]
%\node[anchor=north west,inner sep=0pt] at (0,0) {\includegraphics[width=\paperwidth]{figures/back5.jpg}}; % Background image
\draw[anchor=north] (midpoint) node [fill=titleback!60!white,fill opacity=0.8,text opacity=1,inner sep=1cm]{\Huge\centering\bfseries\sffamily\parbox[c][][t]{1.1\paperwidth}{\centering R für die sozioökonomische Forschung\\[15pt] % Book title
%{\Large }\\[20pt] % Subtitle
{\huge Claudius Gräbner}\\{\small Version 0.9.2}}}; % Author name
\end{tikzpicture}};
\end{tikzpicture}
\vfill
%\endgroup
%\end{titlepage}

\newpage
~\vfill
\thispagestyle{empty}

\noindent Copyright \copyright\ 2020 Claudius Gräbner\\ % Copyright notice
% Image by <a href="https://pixabay.com/users/passagere-1215412/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=990115">MarieSylvie Degueurce</a> from <a href="https://pixabay.com/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=990115">Pixabay</a>
% \noindent \textsc{Published by Publisher}\\ % Publisher

\noindent Web: \href{https://graebnerc.github.io/RforSocioEcon/}{graebnerc.github.io/RforSocioEcon}\\ % URL

\noindent Autor: Claudius Gräbner ist Post-Doc am Institut für Sozioökonomie der
Universität Duisburg-Essen und dem Institut für die Gesamtanalyse der Wirtschaft
der Johannes Kepler Universität Linz. Weitere Infos finden Sie auf seiner
akademischen Homepage: \href{https://claudius-graebner.com/}{www.claudius-graebner.com}.\\ % URL

\noindent Title cover by \href{https://pixabay.com/users/insspirito-1851261/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=1280089}{Garik Barseghyan} from \href{https://pixabay.com/?utm_source=link-attribution&amp;utm_medium=referral&amp;utm_campaign=image&amp;utm_content=1280089}{Pixabay}\\

\includegraphics[]{figures/license.png}

\noindent This work is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License (the ``License''). You may not use this file except in compliance with the License. You may obtain a copy of the License at \url{https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode}. Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an \textsc{``as is'' basis, without warranties or conditions of any kind}, either express or implied. See the License for the specific language governing permissions and limitations under the License.\\ % License information

\noindent \textit{Current version: 0.9.2, Dezember 2020} % Printing/edition date
\newpage
\pagenumbering{arabic}
